Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-08-28 manuscript/main.tex
updated rest of ms
fixed two typos
NSF acknowledgement in manuscript

\title{Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse}
\date{\today}
\author{Fridolin Linder, Bruce Desmarais, Matt Burgess, Eugenia Giraudi}

@@

>>>>

\title{Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse}
\date{\today}
\author{Fridolin Linder, Bruce Desmarais, Matthew Burgess, Eugenia
Giraudy\footnote{This work was supported by National Science Foundation grants
SES-1558661, SES-1619644, CISE-
1320219 and DGE-1144860. Any opinions, findings, and conclusions or
recommendations are those of the
authors and do not necessarily reflect those of the sponsor.}}

@@

%\clearpage
